---
title: "《数学实践》作业五"
author: "许乐乐"
documentclass: ctexart
output:
  rticles::ctex:
    latex_engine: xelatex
    includes:
      in_header: header.tex
      before_body: doc_prefix.tex
      after_body: doc_suffix.tex
    toc: false
    toc_depth: 2
    fig_caption: yes
    number_sections: yes
    keep_tex: true
    df_print: default
    citation_package: natbib
classoption: "hyperref,UTF8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE, fig.showtext = TRUE)
```
```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

We continue working with the World Top Incomes Database [https://wid.world], and the Pareto distribution, as in the lab.  We also continue to practice working with data frames, manipulating data from one format to another, and writing functions to automate repetitive tasks.

We saw in the lab that if the upper tail of the income distribution followed a perfect Pareto distribution, then
\begin{eqnarray}
\label{eqn:1percent-vs-0.1-percent}
\left(\frac{P99}{P99.9}\right)^{-a+1}  & = & 10\\
\left(\frac{P99.5}{P99.9}\right)^{-a+1} & = & 5\\
\left(\frac{P99}{P99.5}\right)^{-a+1} & = & 2
\label{eqn:1percent-vs-0.5-percent}
\end{eqnarray}
We could estimate the Pareto exponent by solving any one of these equations for $a$; in lab we used
\begin{equation}
a = 1 - \frac{\log{10}}{\log{(P99/P99.9)}} ~,
\label{eqn:exponent-from-quantile-ratio}
\end{equation}

Because of measurement error and sampling noise, we can't find find one value of $a$ which will work for all three equations \eqref{eqn:1percent-vs-0.1-percent}--\eqref{eqn:1percent-vs-0.5-percent}.  Generally, trying to make all three equations come close to balancing gives a better estimate of $a$ than just solving one of them.  (This is analogous to finding the slope and intercept of a regression line by trying to come close to all the points in a scatterplot, and not just running a line through two of them.)


1. We estimate $a$ by minimizing
\[
\left(\left(\frac{P99}{P99.9}\right)^{-a+1} - 10\right)^2 + \left(\left(\frac{P99.5}{P99.9}\right)^{-a+1} - 5\right)^2 +  \left(\left(\frac{P99}{P99.5}\right)^{-a+1} - 2\right)^2
\]
Write a function, `percentile_ratio_discrepancies`, which takes as inputs `P99`, `P99.5`, `P99.9` and `a`, and returns the value of the expression above.  Check that when `P99=1e6`, `P99.5=2e6`, `P99.9=1e7` and `a=2`, your function returns `0`.
```{r}
percentile_ratio_discrepancies<-function(p99,p99.5,p99.9,a){
  return(((p99/p99.9)^(-a+1)-10)^2+((p99.5/p99.9)^(-a+1)-5)^2+((p99/p99.5)^(-a+1)-2)^2)
}
percentile_ratio_discrepancies(1e6,2e6,1e7,2)
```

2. Write a function, `exponent.multi_ratios_est`, which takes as inputs `P99`, `P99.5`, `P99.9`, and estimates `a`.  It should minimize your `percentile_ratio_discrepancies` function.  The starting value for the minimization should come from \eqref{eqn:exponent-from-quantile-ratio}.  Check that when `P99=1e6`, `P99.5=2e6` and `P99.9=1e7`, your function returns an `a` of 2.
```{r}
exponent.multi_ratios_est<-function(p99,p99.5,p99.9){
  start=1-log(10)/log(p99/p99.9)
  result<-nlm(percentile_ratio_discrepancies,start,p99,p99.5,p99.9)
  return(result$estimate)
}
exponent.multi_ratios_est(1e6,2e6,1e7)
```

3. Write a function which uses  `exponent.multi_ratios_est` to estimate $a$ for the US for every year from 1913 to 2012.  (There are many ways you could do thi, including loops.)  Plot the estimates; make sure the labels of the plot are appropriate.
```{r}
wtid<-read.csv("data/wtid-report.csv")
P99 <- wtid$P99.income.threshold 
P99.5 <- wtid$P99.5.income.threshold 
P99.9 <- wtid$P99.9.income.threshold 
a_est <- c() 
for (i in 1:nrow(wtid)) { 
  a_est[i] <- exponent.multi_ratios_est(P99[i], P99.5[i], P99.9[i]) 
}
plot(a_est~wtid$Year,main="estimate a for the US for every year from 1913 to 2012",xlab="Year",ylab="eatimate a")
```

4. Use \eqref{eqn:exponent-from-quantile-ratio} to estimate $a$ for the US for every year.  Make a scatter-plot of these estimates against those from problem 3.  If they are identical or completely independent, something is wrong with at least one part of your code.  Otherwise, can you say anything about how the two estimates compare?
```{r}
a_est2<-1-log(10)/log(P99/P99.9)
plot(a_est2~a_est,main="Relationship between two groups of estimate a",xlab="estimate a from problem 3",ylab="estimate a from problem 4")
curve(x*1,add=TRUE,col="red")
```
It’s easy to see that two groups of estimate a (from problem 3 and problem 4) are strongly correlated but not identical. Their correlation is positive and they ﬂuctuate around y = x.
