---
title: "《数学实践》作业二"
author: "许乐乐"
documentclass: ctexart
output:
  rticles::ctex:
    latex_engine: xelatex
    includes:
      in_header: header.tex
      before_body: doc_prefix.tex
      after_body: doc_suffix.tex
    toc: false
    toc_depth: 2
    fig_caption: yes
    number_sections: yes
    keep_tex: true
    df_print: default
    citation_package: natbib
classoption: "hyperref,UTF8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE, fig.showtext = TRUE)
```

The data set calif_penn_2011.csv contains information about the housing stock of California and Pennsylvania, as of 2011.  Information as aggregated into "Census tracts", geographic regions of a few thousand people which are supposed to be fairly homogeneous economically and socially.

```{r}
library(tidyverse)
library(ggplot2)
```

1. _Loading and cleaning_
    a. Load the data into a dataframe called `ca_pa`.
```{r}
ca_pa<-read.csv("data./calif_penn_2011.csv")
```

    b. How many rows and columns does the dataframe have?
```{r}
dim(ca_pa)
```
    
    c. Run this command, and explain, in words, what this does:
```
colSums(apply(ca_pa,c(1,2),is.na))
```
```{r}
colSums(apply(ca_pa,c(1,2),is.na))
```
apply(ca_pa,c(1,2),is.na)表示把is.na这个查找缺省值的函数应用到数据集ca_pa的行和列（c(1,2)中,1表示行，2表示列）。colSums()表示对列求和。因此结果显示该数据集中每列中有多少数据是NA。
    d. The function `na.omit()` takes a dataframe and returns a new dataframe, omitting any row containing an NA value.  Use it to purge the data set of rows with incomplete data.
```{r}
ca_pa<-na.omit(ca_pa)
```
    
    e. How many rows did this eliminate?
```{r}
dim(read.csv("data./calif_penn_2011.csv"))[1]-dim(ca_pa)[1]
```
    
    f. Are your answers in (c) and (e) compatible? Explain.
不一致。因为(c)中计算的是每列有几个NA数据，(e)中计算的是至少含有一个NA数据的行数。

2. _This Very New House_  
    a. The variable `Built_2005_or_later` indicates the percentage of houses in each Census tract built since 2005.  Plot median house prices against this variable.
```{r}
attach(ca_pa)
ggplot(ca_pa) +
  geom_point(aes(x=Built_2005_or_later,y=Median_house_value))
```
```{r}
ca_pa%>%
  group_by(Built_2005_or_later)%>%
  summarize(median_hv=mean(Median_house_value))%>%
  ggplot(aes(Built_2005_or_later,median_hv))+
  geom_point()+
  geom_smooth()
```
    
    b. Make a new plot, or pair of plots, which breaks this out by state.  Note that the state is recorded in the `STATEFP` variable, with California being state 6 and Pennsylvania state 42.
```{r}
ggplot(ca_pa)+
  geom_point(aes(x=Built_2005_or_later,y=Median_house_value,color=STATEFP))
```
```{r}
STATEFP<-as.factor(STATEFP)

ca_pa%>%
  group_by(Built_2005_or_later,STATEFP)%>%
  summarise(median_hv=mean(Median_house_value))%>%
  ggplot(aes(Built_2005_or_later,median_hv,color=STATEFP))+
  geom_point()+
  geom_smooth()
```

```{r}
ggplot(ca_pa)+
  geom_point(aes(x=Built_2005_or_later,y=Median_house_value))+
  facet_wrap(~STATEFP)
```
    
3. _Nobody Home_  
The vacancy rate is the fraction of housing units which are not occupied.  The dataframe contains columns giving the total number of housing units for each Census tract, and the number of vacant housing units.  
    a. Add a new column to the dataframe which contains the vacancy rate.  What are the minimum, maximum, mean, and median vacancy rates?
```{r}
ca_pa <- ca_pa %>%
  mutate(vacancy_rate=Vacant_units/Total_units)
min(ca_pa[,"vacancy_rate"])
max(ca_pa[,"vacancy_rate"])
mean(ca_pa[,"vacancy_rate"])
median(ca_pa[,"vacancy_rate"])
summary(ca_pa$vacancy_rate)
```
    
    b. Plot the vacancy rate against median house value.
```{r}
ggplot(ca_pa)+
  geom_point(aes(x=Median_house_value,y=vacancy_rate))
```
    
    c. Plot vacancy rate against median house value separately for California and for Pennsylvania.  Is there a difference?
```{r}
ggplot(ca_pa)+
  geom_point(aes(x=Median_house_value,y=vacancy_rate))+
  facet_wrap(~STATEFP)
```
    YES.(with California being state 6 and Pennsylvania state 42.)Pennsylvania的图在左下角集中，房价中位数较低，较高房价的空房率较低。而California的图对于房价中位数较为散布，房价中位数有高有低。
    
4. The column `COUNTYFP` contains a numerical code for counties within each state.  We are interested in Alameda County (county 1 in California), Santa Clara (county 85 in California), and Allegheny County (county 3 in Pennsylvania).
    a. Explain what the block of code at the end of this question is supposed to accomplish, and how it does it.
    ```{r, eval=FALSE}
acca <- c()
for (tract in 1:nrow(ca_pa)) {
  if (ca_pa$STATEFP[tract] == 6) {
    if (ca_pa$COUNTYFP[tract] == 1) {
      acca <- c(acca, tract)
    }
  }
}
accamhv <- c()
for (tract in acca) {
  accamhv <- c(accamhv, ca_pa[tract,10])
}
median(accamhv)
```
    先通过遍历ca_pa的行，通过查找STATEFP为6并且COUNTYFP为1的国家Santa Clara，将这些观测值存储到向量acca中。再提取Santa Clara的每条数据的第十列Median_house_value房价中位数到向量accamhv中，并计算均值，从而得到Santa Clara该国的Median_house_value的中位数。
    
    b. Give a single line of R which gives the same final answer as the block of code.  Note: there are at least two ways to do this; you just have to find one.
```{r}
ca_pa%>%
  filter(STATEFP==6,COUNTYFP==1)%>%
  dplyr::select(10)%>% 
  unlist()%>% 
  median()
```
    
    c. For Alameda, Santa Clara and Allegheny Counties, what were the average percentages of housing built since 2005?
```{r}
ca_pa%>%
  filter(STATEFP==6,COUNTYFP==1)%>%
  select("Built_2005_or_later")%>%
  unlist()%>%
  mean()
ca_pa%>%
  filter(STATEFP==6,COUNTYFP==85)%>%
  select("Built_2005_or_later")%>%
  unlist()%>%
  mean()
ca_pa%>%
  filter(STATEFP==42,COUNTYFP==3)%>%
  select("Built_2005_or_later")%>%
  unlist()%>%
  mean()
```
```{r}
ca_2005<-
  ca_pa%>%
  filter((STATEFP==42&COUNTYFP==3)|(STATEFP==6&(COUNTYFP%in%c(1,85))))%>%
  group_by(COUNTYFP)%>%
  summarise(mean_2005=mean(Built_2005_or_later))
ca_2005
```
    
    d. The `cor` function calculates the correlation coefficient between two variables.  What is the correlation between median house value and the percent of housing built since 2005 in (i) the whole data, (ii) all of California, (iii) all of Pennsylvania, (iv) Alameda County, (v) Santa Clara County and (vi) Allegheny County?
```{r}
mycor<-function(d){
  return(cor(d$Median_house_value,d$Built_2005_or_later))
}
mycor(ca_pa)
ca_pa%>%
  filter(STATEFP==6)%>%
  mycor()
ca_pa%>%
  filter(STATEFP==42)%>%
  mycor()
ca_pa%>%
  filter(STATEFP==6,COUNTYFP==1)%>%
  mycor()
ca_pa%>%
  filter(STATEFP==6,COUNTYFP==85)%>%
  mycor()
ca_pa%>%
  filter(STATEFP==42,COUNTYFP==3)%>%
  mycor()
```
    
    e. Make three plots, showing median house values against median income, for Alameda, Santa Clara, and Allegheny Counties.  (If you can fit the information into one plot, clearly distinguishing the three counties, that's OK too.)
```{r}
library(ggpubr)
p1<-ca_pa%>%filter(STATEFP==6,COUNTYFP==1)%>%
  ggplot(aes(Median_household_income,Median_house_value))+
  geom_point()+ggtitle("Alameda")
p2<-ca_pa%>%filter(STATEFP==6,COUNTYFP==85)%>%
  ggplot(aes(Median_household_income,Median_house_value))+
  geom_point()+ggtitle("Santa Clara")
p3<-ca_pa%>%filter(STATEFP==42,COUNTYFP==3)%>%
  ggplot(aes(Median_household_income,Median_house_value))+
  geom_point()+ggtitle("Allegheny")
ggarrange(p1,p2,p3,ncol=3,nrow=1)
```

MB.Ch1.11. Run the following code:
```{r}
gender <- factor(c(rep("female", 91), rep("male", 92)))
table(gender)
gender <- factor(gender, levels=c("male", "female"))
table(gender)
gender <- factor(gender, levels=c("Male", "female"))
# Note the mistake: "Male" should be "male"
table(gender)
table(gender, exclude=NULL)
rm(gender)  # Remove gender
```
Explain the output from the successive uses of table().
table()使用交叉分类引自来建立每个因子水平组合的计数列联表。
第一行：将性别作为一个因子factor，具有两个水平level:female和male。
第二行：调换了两个水平的顺序。
第三行：将level重定义为Male和female，但是Male未赋值默认为0。
第四行：输出其他值92，为原来male的计数。
     
MB.Ch1.12. Write a function that calculates the proportion of values in a vector x that exceed some value cutoff.

(a) Use the sequence of numbers 1, 2, . . . , 100 to check that this function gives the result that is expected.
```{r}
cal_pro<-function(vec,cut){
  return(sum(vec>cut)/length(vec))
}
seq100<-seq(1,100)
cal_pro(seq100,50)
```

(b) Obtain the vector ex01.36 from the Devore6 (or Devore7) package. These data give the times required for individuals to escape from an oil platform during a drill. Use dotplot() to show the distribution of times. Calculate the proportion of escape times that exceed 7 minutes.
```{r}
library(Devore7)
dotplot(ex01.36)
cal_pro(unlist(ex01.36),7*60)
```

MB.Ch1.18. The Rabbit data frame in the MASS library contains blood pressure change measurements on five rabbits (labeled as R1, R2, . . . ,R5) under various control and treatment conditions. Read the help file for more information. Use the unstack() function (three times) to convert Rabbit to the following form:

Treatment Dose   R1   R2   R3   R4   R5 

1 Control 6.25  0.50 1.00 0.75 1.25 1.5 

2 Control 12.50 4.50 1.25 3.00 1.50 1.5 

....
```{r}
attach(Rabbit)
Dose <- unstack(Rabbit, Dose ~ Animal)[,1]
Treatment <- unstack(Rabbit, Treatment ~ Animal)[,1]
BPchange <- unstack(Rabbit, BPchange ~ Animal)
Rabbit.df <- data.frame(Treatment, Dose, BPchange)
Rabbit.df
```

