---
title: "《数学实践》作业一"
author: "许乐乐"
documentclass: ctexart
output:
  rticles::ctex:
    latex_engine: xelatex
    includes:
      in_header: header.tex
      before_body: doc_prefix.tex
      after_body: doc_suffix.tex
    toc: false
    toc_depth: 2
    fig_caption: yes
    number_sections: yes
    keep_tex: true
    df_print: default
    citation_package: natbib
classoption: "hyperref,UTF8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE, fig.showtext = TRUE)
```

1. The Iowa data set iowa.csv is a toy example that summarises the yield of wheat (bushels per acre) for the state of Iowa between 1930-1962. In addition to yield, year, rainfall and temperature were recorded as the main predictors of yield.
    a. First, we need to load the data set into R using the command `read.csv()`. Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called `iowa.df`.
    b. How many rows and columns does `iowa.df` have? 
    c. What are the names of the columns of `iowa.df`?
    d. What is the value of row 5, column 7 of `iowa.df`?
    e. Display the second row of `iowa.df` in its entirety.
```{r}
# ?read.csv ## Use the help function to learn what arguments this function takes.
library(tidyverse)
library(DAAG)
iowa.df<-read.csv("data/Iowa.csv",header=T,sep=";")
dim(iowa.df)
```
Solution: iowa.df has 33 rows and 10 columns.

```{r}
names(iowa.df)
```

Solution: the names of the columes of iowa.df are [1] "Year"  "Rain0" "Temp1" "Rain1" "Temp2"
[6] "Rain2" "Temp3" "Rain3" "Temp4" "Yield"

```{r}
iowa.df[5,7]
```

```{r}
iowa.df[2,]
```


2. Syntax and class-typing.
    a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.

```
vector1 <- c("5", "12", "7", "32")
max(vector1)
sort(vector1)
sum(vector1)
```

    b. For the next series of commands, either explain their results, or why they should produce errors.

```
vector2 <- c("5",7,12)
vector2[2] + vector2[3]

dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]

list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
list4[2]+list4[4]
```

```{r}
vector1 <- c("5", "12", "7", "32") 
max(vector1) 
sort(vector1) 
# sum(vector1)
# Error in sum(vector1) : 'type'(character)参数不对
```

vector1是一个字符串向量。因为向量中的元素是字符串，所以在比较大小时，会先按照第一个字符的大小进行排序，所以在求最大值max()和排序sort()时可以正常执行。而字符串无法按照数字格式进行求和，因此求和sum()不能正常执行。

```{r}
vector2 <- c("5",7,12)
# vector2[2] + vector2[3]
# Error in vector2[2] + vector2[3] : 二进列运算符中有非数值参数
```

```{r}
vector2[2]
is.character(vector2[2])
```

vector2的第一个元素是字符串格式，在同一个向量vector中各个元素的类型需要保持一致，因此第二、三个元素也为字符串格式。所以不能像数字格式那样进行加减运算。

```{r}
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]
```

```{r}
dataframe3[1,1]
is.character(dataframe3[1,1])
dataframe3[1,2]
is.character(dataframe3[1,2])
```

数据框dataframe允许内部元素的类型不同。因此dataframe3中第一个元素是字符串；第二个元素和第三个元素是数值，可以进行加减运算。

```{r}
list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
# list4[2]+list4[4]
# Error in list4[2] + list4[4] : 二进列运算符中有非数值参数
```

```{r}
list4[1]
list4[[1]]
```

列表list允许内部元素的类型不一样。用双括号[[]]取元素时，得到的是元素本身；用单括号[]取元素时，得到的是元素名和元素本身。因此元素本身为数值型的可以进行加减运算，而元素名和元素本身的结合体无法进行加减运算。

3. Working with functions and operators.
    a. The colon operator will create a sequence of integers in order. It is a special case of the function `seq()` which you saw earlier in this assignment. Using the help command `?seq` to learn about the function, design an expression that will give you the sequence of numbers from 1 to 10000 in increments of 372. Design another that will give you a sequence between 1 and 10000 that is exactly 50 numbers in length.
    b. The function `rep()` repeats a vector some number of times. Explain the difference between `rep(1:3, times=3) and rep(1:3, each=3).
    
```{r}
seq(1,10000,by=372)
seq(1,10000,length.out=50)
```

```{r}
rep(1:3,times=3)
rep(1:3,each=3)
```

times=3是将所有元素整体循环三次；each=3是将逐个元素循环三次。

MB.Ch1.2. The orings data frame gives data on the damage that had occurred in US space shuttle launches prior to the disastrous Challenger launch of 28 January 1986. The observations in rows 1, 2, 4, 11, 13, and 18 were included in the pre-launch charts used in deciding whether to proceed with the launch, while remaining rows were omitted.

Create a new data frame by extracting these rows from orings, and plot total incidents against temperature for this new data frame. Obtain a similar plot for the full data set.
```{r}
attach(orings)
new1<-orings[c(1,2,3,11,13,18),]
plot(new1$Temperature,new1$Total)
```

```{r}
plot(Temperature,Total)
```

MB.Ch1.4. For the data frame ais (DAAG package)

(a) Use the function `str()` to get information on each of the columns. Determine whether any of the columns hold missing values.
```{r}
str(ais)
which(colSums(is.na(ais))>0)
```

ais没有缺失值。

(b) Make a table that shows the numbers of males and females for each different sport. In which sports is there a large imbalance (e.g., by a factor of more than 2:1) in the numbers of the two sexes?

```{r}
attach(ais)
table(sport,sex)
rate<-table(sport,sex)[,1]/table(sport,sex)[,2]
rate
subset(rate, rate<0.5| rate>2)
```

有重大性别差异的运动：Gym   Netball   T_Sprnt    W_Polo

MB.Ch1.6.Create a data frame called Manitoba.lakes that contains the lake’s elevation (in meters above sea level) and area (in square kilometers) as listed below. Assign the names of the lakes using the `row.names()` function.

```{r}
row.names(Manitoba.lakes)
```

(a) Use the following code to plot `log2(area)` versus elevation, adding labeling information (there is an extreme value of area that makes a logarithmic scale pretty much essential):

```{r}
attach(Manitoba.lakes)
plot(log2(area) ~ elevation, pch=16, xlim=c(170,280))
# NB: Doubling the area increases log2(area) by 1.0
text(log2(area) ~ elevation, labels=row.names(Manitoba.lakes), pos=4)
text(log2(area) ~ elevation, labels=area, pos=2) 
title("Manitoba's Largest Lakes")
```

Devise captions that explain the labeling on the points and on the y-axis. It will be necessary to explain how distances on the scale relate to changes in area.

(b) Repeat the plot and associated labeling, now plotting area versus elevation, but specifying `ylog=TRUE` in order to obtain a logarithmic y-scale.
```{r}
plot(area ~ elevation, pch=16, xlim=c(170,280), ylog=T)
text(area ~ elevation, labels=row.names(Manitoba.lakes), pos=4, ylog=T)
text(area ~ elevation, labels=area, pos=2, ylog=T) 
title("Manitoba's Largest Lakes")
```

MB.Ch1.7. Look up the help page for the R function `dotchart()`. Use this function to display the areas of the Manitoba lakes (a) on a linear scale, and (b) on a logarithmic scale. Add, in each case, suitable labeling information.

(a) on a linear scale
```{r}
dotchart(Manitoba.lakes$area,labels=row.names(Manitoba.lakes),xlab="area")
```

(b) on a logarithmic scale
```{r}
dotchart(Manitoba.lakes$area,labels=row.names(Manitoba.lakes),xlab="area",log="x")
```

MB.Ch1.8. Using the `sum()` function, obtain a lower bound for the area of Manitoba covered by water.
```{r}
sum(Manitoba.lakes[,"area"])
```

